---
title: "Airbnb Dataset Analysis"
author: "Sonali"
date: "2025-03-30"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Introduction

In this assignment, we are performing a data analysis on an Airbnb dataset using R Programming.  
The objective of this assignment is to apply basic data manipulation techniques on the dataset.  
We will perform two tasks:
1. Reorder the dataset rows in descending order based on a numeric column.
2. Rename selected column names for better clarity.

##Load Libraries and Dataset

In this section, we will load the required library and the Airbnb dataset.  
We will use the `dplyr` package for data manipulation and load the dataset from the local folder.

```{r}
# Install dplyr package (only one time)
# install.packages("dplyr")

# Load library
library(dplyr)

# Load dataset
airbnb_data <- read.csv("Airbnb_Sample.csv.csv", check.names = FALSE)

# View column names
colnames(airbnb_data)
```

## Task 1: Reorder Multiple Rows in Descending Order

In this task, we will reorder the rows of the Airbnb dataset in descending order based on the `price` column.  
This will help us to see the listings with the highest prices at the top of the dataset.

```{r}
# Reorder rows in descending order by price
airbnb_sorted <- airbnb_data %>%
  arrange(desc(price))

# View top 10 rows after sorting
head(airbnb_sorted, 10)
```

## Task 2: Rename Some of the Column Names

In this task, we will rename some of the column names in the Airbnb dataset to make them clearer.  
The following changes will be made:
- `NAME` will be renamed to `listing_name`
- `price` will be renamed to `listing_price`
- `host id` will be renamed to `host_id_number`

```{r}
# Rename selected column names
airbnb_renamed <- airbnb_data %>%
  rename(
    listing_name = NAME,
    listing_price = price,
    host_id_number = `host id`
  )

# View new column names
colnames(airbnb_renamed)
```

## Conclusion

In this assignment, we successfully performed basic data manipulation tasks using R Programming on the Airbnb dataset.  
We reordered the dataset rows in descending order based on the `price` column and renamed selected column names to improve clarity.

---

  

