---
Title: "Task 4 - AirBnb Data Analysis"
Author: Akshat Singh
Date: "2025-03-31"
Output:
  pdf_document: default
    df_print: paged
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is Task 4 of the AirBnb Data Analysis our group has been conducting. In this task we had to choose a variable of our choice from the dataset and define a user defined function for the same variable.

We have used the Construction Year as our variable to print information of all the propertied listed and constructed after 2020.

Below is the code for the same Task.

```{r cars}
getwd()
Airbnb_Open_Data <- read.csv("/cloud/project/Airbnb_Open_Data.csv", header=FALSE)
recent_properties <- as.numeric(Airbnb_Open_Data$V15)
recent_properties <- Airbnb_Open_Data[Airbnb_Open_Data$V15 > 2020, ]
print(recent_properties)

```

**Title: "Task 5 - AirBnb Data Analysis"**

In this task we were supposed to filter data regarding cancellation policy based on the location of the property.

For this output we had set a condition for Brooklyn and hence it showed us the date of the property as well as the cancellation policy of the particular BnB.

The code for the function is given below.

```{r cars2}
install.packages("dplyr")
library(dplyr)
Airbnb_Open_Data$V15 <- as.numeric(Airbnb_Open_Data$V15)
brooklyn_new_properties <- Airbnb_Open_Data %>%
  filter(Airbnb_Open_Data$V15 > 2010, Airbnb_Open_Data$V6 == "Brooklyn") %>%
  select(V15,V13)
print(brooklyn_new_properties)
```

## Including Plots

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
