---
title: "AirbnbDataset_Analysis"
author: "Sohini Biswas"
date: "2025-03-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```


# AUTHOR - SOHINI BISWAS

setwd("C:\\Users\\sohin\\Downloads")

getwd()

airbnb_data <- read.csv("airbnb_Data.csv", check.names = FALSE)

#   TASK 1 : Remove Missing Values in the Dataset
#   Check for missing values in each column
missing_values_per_column <- colSums(is.na(airbnb_data))
print("Missing values per column:")
print(missing_values_per_column)

#   Total missing values in the entire dataset
total_missing_values <- sum(is.na(airbnb_data))
print(paste("Total missing values:", total_missing_values))

#   Remove rows with any missing values
airbnb_cleaned_rows <- na.omit(airbnb_data)

#   Remove columns with any missing values
airbnb_cleaned_cols <- airbnb_data[, colSums(is.na(airbnb_data)) == 0]

#   TASK 2 : Identify and remove Duplicate Values in the Dataset
#   Identify duplicate rows
duplicate_rows <- duplicated(airbnb_data)

#   Count the number of duplicate rows
number_of_duplicate_rows <- sum(duplicate_rows)
print(paste("Number of duplicate rows:", number_of_duplicate_rows))

#   View the duplicate rows
print("Duplicate rows:")
print(airbnb_data[duplicate_rows, ])

#   Remove duplicate rows
airbnb_unique <- airbnb_data[!duplicate_rows, ]

#   Verify removal by counting rows before and after
print(paste("Number of rows before removing duplicates:", nrow(airbnb_data)))
print(paste("Number of rows after removing duplicates:", nrow(airbnb_unique))


